Conference Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2021-03-11 paper/main.tex
starting general architecture

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

@@

As we already said, the architecture implemented is different from the usually provided by this type of system, also because the modern infrastructure relies on cloud computing or external services. Our implementation do not share information about the user, and keeps all the data in the main server, eventually providing the possibility to accessed from outside. Anyway, in this case is not true that a cloud-computing is better, even if is more scalable, if there is no power available at home, the plugs will not be managed correctly either in a decentralized infrastructure. Even worse in a cloud based system, the plugs could not work properly, if there is no internet connection. 

>>>>

\begin{IEEEkeywords}
Domotic plugs; ADD MORE HERE
\end{IEEEkeywords}

@@

The architecture implemented differs from the most common architectures used in this scenario in two major aspects, first most homes don't have this kind of system even in place, instead a circuit breaker triggers for safety reasons when too much power is being consumed. Second, when a similar system is used it usually relies on cloud computing or external services. In contrast our system offers the functionalities already described and both computing and data storage are done locally. This can be an advantage in terms of both privacy and security. Furthermore, this is in advantage in terms of reliability: our system doesn't need an internet connection to properly work, instead it just needs a working WLAN. However, while this aspect is significant, the development of the prototype hasn't focused on the security aspects and security issues will be discussed in the appropriate section. The architecture of the system is such that if need be it can be easily modified to use third party services.
